---
title: "Final project"
author: "Amy Kim"
format: 
html:
theme: sandstone
execute:
	eval: true
	echo: false
	error: true
	
---

This is R bootcamp final project, providing descriptive statistics, regression analysis, and histogram on a prospective, randomized, placebo-controlled clinical trial, Streptomycin Treatment of Pulmonary Tuberculosis. Data source: https://github.com/higgi13425/medicaldata/tree/master/data

```{r}
library(tidyverse)
library(gtsummary)
library(readr)
library(here)

tb <- read_csv(here("strep_tb.csv"))

```


```{r}
#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
table1<-tbl_summary(
	tb,
	by = gender,
	include = c(gender, arm, dose_strep_g, baseline_condition, baseline_cavitation, strep_resistance, improved),
	label = list(
		arm ~ "Group",
		dose_strep_g ~ "Dose of Streptomycin (g)",
		baseline_condition ~ "Patient Condition at Baseline",
		baseline_cavitation ~ "Lung Cavitation at Baseline",
		strep_resistance ~ "Streptomycin Resistance at 6m",
		improved ~ "Outcome of Improved"
	))

```
There were `r inline_text(table1, variable = "gender", column = "F")` female participants in this study.

```{r}
#| label: tbl-regression
#| tbl-cap: "Linear Regression Analysis"

library(broom)

linear_model_int <- lm(improved ~ gender*arm + baseline_condition + baseline_cavitation + strep_resistance,
											 data = tb)
tbl_regression(
	linear_model_int,
	intercept = TRUE,
	label = list(
		gender ~ "Gender",
		arm ~ "Group",
		baseline_condition ~ "Condition of the Patient at Baseline",
		baseline_cavitation ~ "Cavitation of the Lungs at baseline",
		strep_resistance ~ "Resistance to Streptomycin at 6m"
	))
```
@tbl-regression contains results from the linear regression


```{r}
#| label: fig-figure1
#| fig-cap: "Histogram of Chest X-ray Rating at 6m"

hist(tb$rad_num, main = "Rating of Chest X-ray at Month 6",
		 xlab = "Rating",
		 ylab = "Frequency")
```
@fig-figure1 contains a Histogram of Chest X-ray Rating at 6m.


```{r}
#| label: tbl-function
#| tbl-cap: "New Function Table"

new_table_function <- function(model) {
	tbl_regression(
		model,
		intercept = TRUE,
		label = list(
			gender ~ "Gender",
			arm ~ "Group",
			baseline_condition ~ "Condition of the Patient at Baseline",
			baseline_cavitation ~ "Cavitation of the Lungs at baseline",
			strep_resistance ~ "Resistance to Streptomycin at 6m"
		)
	)
}

linear_model_int <- lm(improved ~ gender*arm + baseline_condition + baseline_cavitation + strep_resistance,
											 data = tb)

new_table_function(linear_model_int)
```


```{r}
  mode_value<- mode(tb$rad_num)
```
Mode of Rating of Chest X-ray at Month 6 is `r mode_value`.


```{r}
project_file_path<- here("R","Final project.html")
```

